Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex

However, we can also note that the error increases quite slowly.
The errors obtained comparing $l_1$, or for bigger radii $l_2$ approximations
with the $l_0$ level are small. The errors measured comparing higher levels
are of course much bigger and those level are thus never used in practice.
They are presented here to illustrate how the refining process converges to
the $l_0$ level.
Thanks to this low error, higher approximation levels are visually
very similar to the $l_0$ level. We can therefore use them for exploring our
datasets in real time, changing the radii on the fly and visualising dynamic datasets.

>>>>

However, we can also note that the error increases quite slowly.
The errors obtained comparing $l_1$, or for bigger radii $l_2$ approximations
with the $l_0$ level are small. The errors measured comparing higher levels
are of course much bigger and those level are thus never used in practice.
They are presented here to illustrate how the refining process converges to
the $l_0$ level.

This convergence is shown in Figure \ref{fig:convergence}. It has been evaluated using
two different strategy for volume computation. The first one reads the interpolated
data from the mipmap is adds 1 to the volume if this value is above a threshold. 
The second strategy adds directly to the volume the interpolated data read from the mipmap.
The results are shown Figure \ref{fig:graph_convergence}. It can be seen that the
interpolation done by the mipmap allows the resulting curvature to converge
faster to the $l_0$ level.

Thanks to this low error, higher approximation levels are visually
very similar to the $l_0$ level. We can therefore use them for exploring our
datasets in real time, changing the radii on the fly and visualising dynamic datasets.
